Visual Interrogation of Attention-Based Models for Natural Language Inference and Machine Comprehension

### 2018-05-31 EMNLP-demo-paper/result.tex
fixes

As illustrated in Fig.~\ref{fig:NLIexample}(a), the input sentence pairs (\textbf{P}:``A woman in a green jacket is drinking tea.'' \textbf{H}:``A woman is drinking green tea.'') is predicted to be entailment, which is incorrect.
By examining the attention, we can see the word \emph{green} in ``\emph{green} jacket" is aligned to the \emph{green} in ``\emph{green} tea". However, these two ``green'' decorate different nouns, which lead to the wrong prediction. The grammar structure is captured by the dependency tree, i.e., \emph{green} in \textbf{P} is attached to ``jacket''. However, the model does not has access to the grammar information and mistakenly assume the two \emph{greens} are describing the same thing (thus predict \emph{entailment}). 
%
To correct the mistake, we can edit the attention value and remove the align between these two "green" (see (c)(b)).
As expected, the prediction label is corrected (\emph{neutral}).

>>>>

As illustrated in Fig.~\ref{fig:NLIexample}(a), the input sentence pairs (\textbf{P}:``A woman in a green jacket is drinking tea.'' \textbf{H}:``A woman is drinking green tea.'') is predicted to be \emph{entailment}, which is incorrect.
By examining the attention, we can see the word \emph{green} in ``\emph{green} jacket" is aligned to the \emph{green} in ``\emph{green} tea". However, these two \emph{green}`s decorate different nouns, which potentially lead to the wrong prediction. The grammar structure is visually presented by dependency tree.
%i.e., \emph{green} in \textbf{P} is attached to ``jacket''.
However, the model does not has access to the grammar information and mistakenly assumes the two \emph{greens} are describing the same thing.
% (thus predict \emph{entailment}). 
%
To correct the mistake, we can edit the attention value and remove the align between these two "green" (see (c)(b)).
As expected, the prediction label is corrected (\emph{neutral}).

### 2018-05-31 EMNLP-demo-paper/system.tex
fixes

\subsection{Prediction Visualization}
Efficient visual encoding for prediction is crucial for communicating the model behavior. And to fully support the input perturbation feature, the visual encoding should also allow multiple predictions to be shown in the same visualization.
%
For the natural language inference task, as illustrated in Figure~\ref{fig:prediction}, the predicted probabilities are encoded in the triangle barycentric coordinate, where the vertices represent the three possible predictions (namely, \emph{entail}, \emph{contradict}, and \emph{neutral}). The prediction for the original unperturbed input is illustrated by a larger yellow circle, whereas the prediction of perturbed inputs is represented by smaller grey circles.
A density contour of the prediction is computed to emphasize the highly cluttered areas and detect outliers.

>>>>

\subsection{Prediction Visualization}
Efficient visual encoding for prediction is crucial for communicating the model behavior. And to fully support the input perturbation feature, the visual encoding should also allow multiple predictions to be shown in the same visualization.
%
For the natural language inference task, as illustrated in Figure~\ref{fig:prediction}, the predicted probabilities are encoded in the triangle barycentric coordinate, where the vertices represent the three possible predictions (namely, \emph{entailment}, \emph{contradiction}, and \emph{neutral}). The prediction for the original unperturbed input is illustrated by a larger yellow circle, whereas the prediction of perturbed inputs is represented by smaller grey circles.
A density contour of the prediction is computed to emphasize the highly cluttered areas and detect outliers.
